### 2010-02-18 StatusReport.tex
Added more detail about CAR model without E.

    The CAR model did not converge for any of the data.  Although the standard
    model and the CAR model performed similarly in testing when both models
    converged, the standard model converged much more often than the CAR model
    did.  We think this is because the CAR model attempts to estimate too many
    parameters.  There is a different estimate of \(\theta\) for every site,
    which adds a considerable amount of complexity to the model.  We also tried
    to simplify this model by eliminating E, but this did not improve
    convergence.  Therefore, we are not going to include any estimates of
    parameters from the CAR model in this report.

>>>>

    The CAR model did not converge for any of the data.  Although the standard
    model and the CAR model performed similarly in testing when both models
    converged, the standard model converged much more often than the CAR model
    did.  We think this is because the CAR model attempts to estimate too many
    parameters.  There is a different estimate of \(\theta\) for every site,
    which adds a considerable amount of complexity to the model.  We also tried
    to simplify this model by eliminating E because this was somewhat successful
    with the standard model.  This improved convergence with the 402m data, but
    gave us \(\psi\) estimates greater than 0.9 for all rivers, which does not
    seem reasonable.  Therefore, we are not going to include any estimates of
    parameters from the CAR model in this report.
